### 2021-02-15 README.Rmd
added ropensci in review badge

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/open-AIMS/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/open-AIMS/dataaimsr?branch=master)
![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/open-AIMS/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/open-AIMS/dataaimsr?branch=master)
![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->
